Exploring probability distributions for bivariate temporal granularities

### 2019-08-25 main.Rmd
updating analysis 2 of case study

```{r initial, echo = FALSE, cache = FALSE, include = FALSE}
options("knitr.graphics.auto_pdf" = TRUE)
library(knitr)
library(tidyverse)
library(lubridate)
library(lvplot)
library(ggridges)
opts_chunk$set(
  echo = FALSE, warning = FALSE, message = FALSE, comment = "#>",
  fig.path = "figure/", fig.align = "center", fig.show = "hold",
  cache = TRUE, cache.path = "cache/",
  out.width = ifelse(is_html_output(), "100%", "\\textwidth")
)
knitr::opts_knit$set(root.dir = here::here())
```

@@

One of the customer trial [@smart-meter] conducted as part of the Smart Grid Smart City (SGSC) project (2010-2014) in NewCastle, New South Wales and some parts of Sydney provides customer wise data on half hourly energy usage and detailed information on appliance use, climate, retail and distributor product offers, and other related factors. It would be interesting to explore the energy consumption distribution for these customers and gain more insights on their energy behavior which are otherwise lost either due to aggreagation or looking only at coarser temporal units.

Let us compare the energy consumption distribution for two households from the customer trials.

@@

For the purpose of this analysis. We only take the data for the year 2013. Let us look at the distribution of energy across coarser temporal granularities and then deep dive into finer temporal granularities.

@@

@@

@@

data_sm1 %>% granplot("month_year", "day_week", response = "general_supply_kwh", plot_type = "lv", quantile_prob = c(0.1, 0.25, 0.5, 0.75, 0.9)) +  ggtitle("LV plot of energy consumption across hours of day by month of years for Household 1")+ scale_y_continuous(breaks = seq(0, 1.5, 0.25))
```

data_sm3 %>% granplot("month_year", "day_week", response = "general_supply_kwh", plot_type = "lv") +  ggtitle("LV plot of energy consumption across hours of day by month of years for Household 3")+ scale_y_continuous(breaks = seq(0, 1.5, 0.25))
```

```{r cust1_hour-day_day-week}
data_sm1 %>% granplot("day_week", "hour_day", "general_supply_kwh", plot_type = "decile") +  ggtitle("Boxplot of energy consumption for Customer 1")
```
<!-- # ``````{r cust2_hour-day_day-week} -->
<!-- # data_sm2 %>% granplot("day_week", "hour_day", "general_supply_kwh", plot_type = "quantile") + ggtitle("Boxplot of energy consumption for Customer 2") -->
<!-- # ``` -->

``````{r cust3_hour-day_day-week}
data_sm3 %>% granplot("day_week", "hour_day", "general_supply_kwh", plot_type = "decile") + ggtitle("Boxplot of energy consumption for Customer 3")
```

>>>>

```{r initial, echo = FALSE, cache = FALSE, include = FALSE}
options("knitr.graphics.auto_pdf" = TRUE)
library(knitr)
library(tidyverse)
library(lubridate)
library(lvplot)
library(ggridges)
opts_chunk$set(
  echo = FALSE, warning = FALSE, message = FALSE, comment = "#>",
  fig.path = "figure/", fig.align = "center", fig.show = "hold",
  cache = FALSE, cache.path = "cache/",
  out.width = ifelse(is_html_output(), "100%", "\\textwidth")
)
knitr::opts_knit$set(root.dir = here::here())
```

@@

One of the customer trial [@smart-meter] conducted as part of the Smart Grid Smart City (SGSC) project (2010-2014) in NewCastle, New South Wales and some parts of Sydney provides customer wise data on half hourly energy usage and detailed information on appliance use, climate, retail and distributor product offers, and other related factors. It would be interesting to explore the energy consumption distribution for these customers and gain more insights on their energy behavior which are otherwise lost either due to aggreagation or looking only at coarser temporal units. The idea here is to show how looking at time across different granularities together can help identify different behavioral patterns.

Let us compare the energy consumption distribution for two households from the customer trials. For the purpose of this analysis, we only take the data for the year 2013. Let us look at the distribution of energy across coarser temporal granularities and then deep dive into finer temporal granularities.

@@

@@

```{r cust1_hour-day_day-week}
data_sm1 %>% granplot("day_week", "hour_day", "general_supply_kwh", plot_type = "violin") +  ggtitle("Boxplot of energy consumption for Customer 1")
```
<!-- # ``````{r cust2_hour-day_day-week} -->
<!-- # data_sm2 %>% granplot("day_week", "hour_day", "general_supply_kwh", plot_type = "quantile") + ggtitle("Boxplot of energy consumption for Customer 2") -->
<!-- # ``` -->

``````{r cust3_hour-day_day-week}
data_sm3 %>% granplot("day_week", "hour_day", "general_supply_kwh", plot_type = "violin") + ggtitle("Boxplot of energy consumption for Customer 3")
```

@@

-  Across days of the week by months

```{r cust1_dw_my}
library(ggplot2)

data_sm1 %>% granplot("month_year", "day_week", response = "general_supply_kwh", plot_type = "lv", quantile_prob = c(0.1, 0.25, 0.5, 0.75, 0.9)) +  ggtitle("LV plot of energy consumption across days of week by month of years for Household 1")+ scale_y_continuous(breaks = seq(0, 1.5, 0.25))
```

@@

data_sm3 %>% granplot("month_year", "day_week", response = "general_supply_kwh", plot_type = "lv") +  ggtitle("LV plot of energy consumption across days of week by month of years for Household 3")+ scale_y_continuous(breaks = seq(0, 1.5, 0.25))
```
